\cvsection{Work Experience} % SECTION TITLE
\begin{cventries} % CONTENT
  \cvsimpleentry
    {\textbf{Briswell, Software Engineer - FullStack}} % Job title 
    {Vietnam, May. 2022 - Present} % Date
    {
      \begin{cvitems} % Description
        %Cung cap giai pháp dễ dàng testing, nâng cấp, chuyển đổi công nghệ: Clean architect
        % Đề xuất và led hợp nhất 6project đơn lẻ thành 1 project...
        % Improved user experience: Nhớ thêm vào có bước điều tra, xác định vấn đề và improve...
        \item {Participated in \textbf{upgrading programming language and framework versions}, such as migrating PHP from 5.x to 8.x. This involved identifying deprecated features, analyzing replacement options, and assessing impact levels. Achieved stable and bug-free operation in the production environment after migration.}
        \item {Optimized database performance by improving \textbf{SQL query speed}, tuning indexes, analyzing query plans, and restructuring data, achieving a \textbf{70–90\% faster query execution time}.}
        \item {Contributed to the \textbf{system architecture} by analyzing and recommending suitable AWS services that balanced cost efficiency and performance requirements. Supported the team in designing the overall architecture and ensuring alignment with project goals.}
        \item {Developed reusable and scalable common components using \textbf{Vue 3} and applying the UI library to enhance consistency, increase reusability, and reduce development effort across multiple projects.}
        \item {Beyond monolithic architecture, researched and worked with microservices, \textbf{Domain-Driven Design (DDD)}, RabbitMQ, rate limiting, and designed repository/service layers with clear bounded context separation.}
        \item {Participated in requirement analysis and development of core system features, ensuring stability and quality throughout the product lifecycle. Consistently adhered to \textbf{SOLID} principles to maintain scalability, resulting in cleaner architecture and easier long-term maintenance.}
        \item {Integrated third-party services such as Stripe, Google Maps API, ensuring secure and business-compliant operations.}
        \item {Improved the company's bug review process during project meetings by streamlining workflows, defining clearer review criteria, preparing pre-meeting summaries, and evaluating the impact level of each bug on the project. These enhancements reduced meeting time by 60–70\% (from 1 hour to 20–25 minutes) while maintaining review quality and supporting better lessons learned for future projects.}
        \item {Created and maintained technical documentation, and supported onboarding for new team members.}
        \item {Tech Stacks: Laravel, CakePHP, NodeJS, NestJS, Vue3, AWS.}
      \end{cvitems} 
    }

\end{cventries}
%docker run -u $UID:$GID --rm -v $PWD:/work csmith/awesome-cv-builder